% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{url}
%\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
%\setlength{\headsep}{0pt}
%\setlength{\topskip}{0pt}
%\setlength{\topmargin}{0pt}
%\setlength{\topsep}{0pt}
%\setlength{\partopsep}{0pt}

\begin{document}

\name{Kaustubh Gadkari}
% \address used twice to have two lines of address
\address{1400 W. Elizabeth St. Apt. 221 Fort Collins CO 80521}
\address{(970)261-1699}
\address{kaustubh.gadkari@gmail.com}


\begin{resume}

%\section{OBJECTIVE}       A position in the field of computers with special
%                interests in business applications programming,
%                information processing, and management systems.


\section{EDUCATION}
                {\sl Ph.D.} Computer Science \hfill Spring 2011 - Present\\
                    Colorado State University, Fort Collins, CO 80523\\
                    Network Security Group\\
                    Co-advisers: Dr. Christos Papadopoulos and Dr. Daniel Massey

                {\sl Master's Degree.} Computer Science \hfill Fall 2010\\
                    Colorado State University, Fort Collins, CO 80523
                    
                {\sl Bachelor of Engineering.} Information Technology \hfill Fall 2006\\
                	  University of Pune, Pune, India

\section{EXPERIENCE}
    {\sl Internship} \hfill Summer 2011\\
      Palo Alto Research Center, Palo Alto CA 94304 \\
      \begin{itemize}
      \item Worked on performance measurements of "Content Centric Networking".(\url{http://www.ccnx.org}).
      \item Performance measurements were carried out on PlanetLab (\url{http://www.planet-lab.org/}) and the Open Network
      Laboratory (\url{https://onl.wustl.edu/}).
      \item Compared performance of CCN with TCP as well as CDNs such as CoralCDN.
      \end{itemize}
      

    {\sl Graduate Research Assistant} \hfill Fall 2009 - Present\\
        Colorado State University, Fort Collins CO 80523
        \begin{itemize}  \itemsep -2pt
            \item Interests: Network measurements, routing with reduced tables, content-centric networking.
            \item Researching new designs for reduced forwarding tables.
            \item Studied the use of fingerprinting custom TCP/IP stacks to detect botnets.
            \item Studied the characteristics of TCP resets.
        \end{itemize}
  
   {\sl Graduate Teaching Assistant} \hfill Fall 2008 - Fall 2009\\
        Colorado State University, Fort Collins CO 80523\\
        Have assisted the following courses:
        \begin{itemize}  \itemsep -2pt
            \item CS 457 - Computer Networking and the Internet.
            \item CS 475 - Parallel Programming
            \item CS 155 - Introduction to Unix
            \item CS 156 - Introduction to C, part 1
            \item CS 157 - Introduction to C, part 2
         \end{itemize}

    {\sl NDN Hub Operator} \hfill {Fall 2010 - Present}\\
     	Colorado State University, Fort Collins CO 80523
	\begin{itemize} \itemsep -2pt
		\item Setup and maintain one of the two central hubs of the Named Data
		Networking Testbed.
	\end{itemize}

    {\sl Network Security Lab System Administrator} \hfill Fall 2006 - Present\\
        Colorado State University, Fort Collins CO 80523
        \begin{itemize} \itemsep -2pt
            \item Setup and currently maintain the Network Security Group Lab, 
            consisting of 30 rack mounted servers and 5 desktop computers
            running Ubuntu Linux/FreeBSD and a Cisco router.
            \item Setup and maintain data capture points at a regional ISP, using
            specialized packet capture hardware from Endace.
        \end{itemize}
	 
    {\sl Visiting Lecturer} \hfill 2006\\
        Symbiosis Institute of Computer Studies and Research, Pune, India
        \begin{itemize} \itemsep -2pt
            \item Taught Linux system administration to students pursuing the Master
            of Science (Computer Applications) degree.
        \end{itemize}

    {\sl Undergraduate Research} \hfill Fall 2005 - Fall 2006\\
        SONIX Systems, Pune, India
        \begin{itemize} \itemsep -2pt
            \item Worked on a project to develop a process infrastructure for the Linux kernel to allow
            transparent process migration across cluster nodes.
        \end{itemize}
   
\section{PUBLICATIONS}
            \begin{enumerate}
              \item {\sl A Fresh Look At Scalable Forwarding Through Router FIB Caching}, Kaustubh Gadkari, Dan Massey and 
              Christos Papadopoulos, {\em Under Review, SIGCOMM 2012}
	        
              \item {\sl Dynamics of Prefix Usage at an Edge Router}, Kaustubh Gadkari, Dan Massey and Christos Papadopoulos,
              ${12^{th}}$ Passive and Active Measurements Conference (PAM 2011), March 2011 
	
         		  \item {\sl Fingerprinting Custom Botnet Protocol Stacks}, Steve DiBenedetto, Kaustubh Gadkari, Nicholas Diel,
              Andrea Steiner, Dan Massey and Christos Papadopoulos, Workshop on Secure Network Protocols (NPSec 2010) 
              (in conjunction with ICNP 2010), October 2010
          	 
              \item {\sl Dynamics of RIB Usage at an Edge Router} (Poster), Kaustubh Gadkari, Steve DiBenedetto, 
               Dan Massey and Christos Papadopoulos, ${18^{th}}$ International Conference on Network Protocols (ICNP 2010), October 2010               
             
               \item {\sl Characterizing TCP Resets in Established Connections}, Nicholas Diel, Kaustubh Gadkari, Steve DiBenedetto,
              Andrea Steiner and Christos Papadopoulos, 
              Technical Report {\emph {CS-08-102}}.
             \end{enumerate}

\section{SERVICES}
	\begin{itemize}
                \item Web and Publications Chair, $4^{th}$ Workshop on Secure Network Protocols, 2008
                \item Ad hoc reviewer for conferences/workshops like INFOCOM 2010, GLOBECOM 2011 and NPSec 2008.
                \item Helped organize CANVAS 2008, which was a computer security vulnerability assessment game for undergraduate students.            
         \end{itemize}
         
\section{ACADEMIC MEMBERSHIPS}
	\begin{itemize}
		\item ACM Student Member
		\item IEEE Student Member
		\item Internet Society (ISOC)
		\item Colorado Chapter of the ISOC               
	\end{itemize}
	
%\section{COMPUTER \\ SKILLS}
%        Effective in C/C++, Perl, Java and Python.





%{\sl Business Applications Programmer} \hfill Fall 1990 \\
%                Allied-Signal Bendix Friction Materials Division, 
%                Financial Planning Department, Latham, NY
%                 \begin{itemize}  \itemsep -2pt % reduce space between items
%                 \item Developed four "user friendly" forecasting 
%                    systems each of which produces 18 to 139 
%                    individual reports. 
%                \item   Developed or improved almost all IFPS 
%                    programs used for financial reports. 
%                \end{itemize}


\end{resume}
\end{document}







